The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-03 paper.tex
update

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution with a spectral index 2 and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

>>>>

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\
